Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-26 paper/ms.tex
table and figure updates
update manuscript

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities of \tn.}
		{\it Top:} RV measurements, with best-fit instrument offsets
    and jitter terms included.  The expected scatter from starspots
    based on $v\sin i$ and the photometric modulation amplitude is of
    order 300m$\,$s$^{-1}$.
		{\it Bottom:}
    RV measurements phased to the orbital ephemeris of \pn.  The
    planet is not detected.  The black line shows a circular
    Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:rvs}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

@@

\subsection{The Star}
\label{subsec:star}
\subsubsection{Cluster Membership}
\label{subsec:member}

\tn\ has been reported as a member of \cn\ by multiple independent 
investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
%FIXME FIXME finish these citations
%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed it as
%IC2602

The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
Veloce) is strong; the rotation period and vsini agree with
sub-Pleiades age expected for an IC 2602 member.

@@

Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
reference to the broader \cn\ cluster, as well as its neighborhood.
Cluster members were identified by \citet{cantatgaudin_gaia_2018}
using using Gaia-DR2 positions, proper motions, and parallaxes.  
We included candidate members with formal membership probability
exceeding 10\%.  Save for a few low-mass outliers, most members appear
to be young and coeval.

\tn\ is in its expected position relative to the other members along
the cluster isochrone.  This photometrically limits the presence of
binary companions in the \tn\ system, to a magnitude difference of
perhaps half the brightness of the target star.

Figure~\ref{fig:hr} also suggests that the membership census of \cn\
is incomplete.  We defined the reference ``neighborhood'' as the group
of at most $10^4$ randomly selected non-member stars within 5 standard
deviations of the mean \cn\ right ascension, declination, and
parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
appear above the main sequence, even though they were not identified
as 5-dimensional kinematic members through the unsupervised
\citet{cantat-gaudin_gaia_2018} membership assignment process.

\subsubsection{Position and Kinematics}

We examine the six-dimensional positions and kinematics in greater
depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
defined here identically to as in Figure~\ref{fig:hr}.  The axes
limits for the right ascension, declination, and parallax dimensions
are as in the Gaia archive query.  The axes limits for the proper
motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
75$^{\rm th}$ percentiles, in order to give a sense of the
population's distribution, while excluding outlying points.  The
radial velocities suffer the greatest incompleteness due to the
current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.

Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
existence of the \cn\ open cluster and {\it (ii)} for the membership
of \tn\ within \cn.
The only dimension that could perhaps lead to some worry is the
parallax, as \tn\ is one of the closest \cn\ members reported by
\citet{cantatgaudin_gaia_2018}.
Fortunately, there are independent means of verifying stellar youth.

@@

%NOTE: begs the question... is there a large population of ~30-50 Myr old
% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?

@@

\subsubsection{Literature Membership}
The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
in what they dubbed ``Group 5''.
Analyzing the clusters of \citet{oh_comoving_2017},
\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
WISE photometry with MIST isochrones, and reported stellar masses,
radii, metallicities, ages, distances, and extinction for 9754 stars,
including \tn.
%Bochanski reported:
%logAge 9.38 +0.42 -0.26
%dist 138.3 +7.0 -7.2
%A_v = 0.27 +0.18 - 0.18
%

\tn\ was also listed as a member of ``Theia 92'' by
\citet{kounkel_untangling_2019}.
These authors identified 999 candidate cluster members, and
reported a cluster isochrone age $\log t = 7.55$ with uncertainty
$\approx 0.15\,{\rm dex}$.
They reported an average extinction of Av=0.243 mag.

@@

@@

\subsubsection{Physical}
 (Lstar, Rstar, Teff, Age and Mstar)

@@

Figure~\ref{fig:sed}.
The SED fit, looking really good with rchi2 = 1.6:

@@

@@

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
%\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities of \tn.}
		{\it Top:} RV measurements, with best-fit instrument offsets
    and jitter terms included.  The expected scatter from starspots
    based on $v\sin i$ and the photometric modulation amplitude is of
    order 300m$\,$s$^{-1}$.
		{\it Bottom:}
    RV measurements phased to the orbital ephemeris of \pn.  The
    planet is not detected.  The black line shows a circular
    Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:rvs}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\subsubsection{Physical Characteristics}

@@

@@

Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
\cn\ cluster, and the ``neighborhood'' of spatially nearby stars.
Stars labelled as ``cluster members'' are those reported by
\citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
motions, and parallaxes.  We included candidate members with formal
membership probability exceeding 10\%.  Save for a few low-mass
outliers, most members appear to be young and coeval.

\tn\ is in its expected position relative to the other members along
the cluster isochrone.  This photometrically limits the presence of
binary companions in the \tn\ system, to within perhaps half the
brightness ($\approx0.75$ magnitudes) of the target star.

Figure~\ref{fig:hr} also suggests that the membership census of \cn\
is incomplete.  We defined the reference ``neighborhood'' as the group
of at most $10^4$ randomly selected non-member stars within 5 standard
deviations of the mean \cn\ right ascension, declination, and
parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
appear above the main sequence, even though they were not identified
as 5-dimensional kinematic members through the unsupervised
\citet{cantatgaudin_gaia_2018} membership assignment process.

\subsection{The Star}
\label{subsec:star}

\subsubsection{Membership of \tn\ in \cn}
\label{subsec:member}

\tn\ has been reported as a member of \cn\ by many independent
investigators \citep[{\it
e.g.},][]{Kharchenko_et_al_2013,oh_comoving_2017,cantatgaudin_gaia_2018,damiani_stellar_2019,kounkel_untangling_2019}.
The simplest way to verify the membership is through inspection of the
Gaia DR2 position and kinematics.  Figure~\ref{fig:full_kinematics}
shows the six-dimensional positions and kinematics of \tn, \cn\
members, and nearby stars.  The ``neighborhood'' is defined as in
Figure~\ref{fig:hr}.  The axes limits for the right ascension,
declination, and parallax dimensions are set by being within 5
standard deviations of the mean \cn\ right ascension, declination, and
parallax.  The axes limits for the proper motion and radial velocity
dimensions are set at the 25$^{\rm th}$ and 75$^{\rm th}$ percentiles,
in order to give a sense of the population's distribution, while
excluding outliers.  The radial velocities suffer the greatest
incompleteness due to the current $G\approx12$ magnitude limit of the
Gaia DR2 data processing.

Figure~\ref{fig:full_kinematics} provides strong evidence that \tn\ is
a member of \cn.  The only dimension that could lead to some worry is
the parallax, as \tn\ is one of the closest \cn\ members reported by
\citet{cantatgaudin_gaia_2018}.  Fortunately, there are independent
means of verifying the star's youth.

@@

%NOTE: begs the question... is there a large population of ~30-50 Myr
%old stars for which we could measure the rotation periods, and
%clarify if the scatter of Upper Sco chills out?

@@

@@

\input{stellar_parameters.tex}

@@

 (Lstar, Rstar, Teff, Age and Mstar)

@@

% Figure~\ref{fig:sed}.
Mention The SED fit, looking really good with rchi2 = 1.6:

@@

\input{model_posterior_table.tex}

@@

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
%\input{model_comparison_table.tex}
\clearpage
